\documentclass[10pt,a4paper,sans]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{blue}

%\usepackage[maxnames=10, backend=bibtex8]{biblatex}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.8]{geometry}

\input{personaldata.tex} %Use personaldata_d.tex as template
%\bibliography{publications}

\makeatletter
\name{Lorenzo}{Ferrillo}
\title{Curriculum Vitae}
\email{\@@@email}
\phone[mobile]{\@@@phone}
\phone[fixed]{\@@@homeph}
\extrainfo{Date of birth: 07/01/1995}
\social[github][github.com/llde]{github.com/llde}
\makeatother

%\makeatletter\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}\makeatother

\def\pplus{\texttt{++}}
\def\sharp{\texttt{\#}}

%\renewcommand{\refname}{Research activities and publications}
%\DefineBibliographyExtras{english}{\let\finalandcomma=\empty}
%\newcommand{\pubitem}[1]{
%    \cvitem{\citefield{#1}{year}}{\textbf{\citefield{#1}{title}} (with \citename{#1}{author}), in \textit{\citefield{#1}{booktitle} } }
%}

\begin{document}
    \makecvtitle

    \section{Education}
    \cventry{2022}{Bachelor Degree in Computer Science}{Sapienza University of Rome, Italy}{}{}{
        Final mark: \emph{100/110}\\
        Thesis title: \emph{Rilevamento di vulnerabilità tramite reti neurali a convoluzione}.\\
        Advisors: \emph{Prof. Fabio De Gaspari}.\\
        Description: \emph{We present a system for vulnerability detection using convolutional neural network and scripts to prepare the dataset for training}.
    }

    \section{Computer skills}
    \cvitem{Programming}{
        Fluent in Rust, Python and C.
    }
    \cvitem{}{
        Good knowledge of C\pplus{}, Java  and Intel x86 Assembly programming languages.
    }
    \cvitem{}{
        Knowledge of SQL,  \LaTeX, C\sharp{} and HLSL.
        Basic knowledge in HTML and CSS.
    }
    \cvitem{Development tools}{
        Good knowledge of Git and the Git workflow. 
        My main development tools include JetBrains IDEs (CLion, IntelliJ Idea, PyCharm), Microsoft Visual Studio and Visual Studio Code, Powershell, zsh, Notepad\pplus and Kate.
    }
    \cvitem{Reverse Engineering}{
        Medium knowledge for Disassemblers and decompilers IDA Pro and Cutter (Rizin/Radare2)
    }
    \cvitem{Operating systems}{
        Expert in GNU/Linux, in particular Ubuntu Fedora and Arch Linux distributions. \newline
        Good knowledge of Windows operating systems, in particular Windows 7/8/10. Member of the Windows Insider program. \newline
        Limited knowledge on other Unix OSes, as OSX, WebOS and BSD systems.
    }
    
    \section{University projects}
    \cvitem{Crawly}{A Concurrent Web Crawler made in Java using the JavaFX library (for "Metodology of Programming"). }
    \cvitem{Crypto-Sithis}{A Client/Server program using pseudo-random numbers to crypt files on disk (for "System Programming").}
    \cvitem{311-X}{Software analysis and architecture engineering for a multi-application Uber-like service (for "Software Engineering"). }
    \cvitem{City-builder}{Procedural generation of the buildings of a city, using the yocto-gl library for rendering (for "Computer Graphic)."}
    \section{Personal projects}
    \cvitem{xOBSE}{An injector to extend the engine capabilities for the game "The Elder Scroll 4: Oblivion", using C++ and inline Microsoft Assembly (MASM).}
    \cvitem{TESReloaded}{An extender for TES4: Oblivion, TES5: Skyrim (legacy/oldrim) and Fallout: New Vegas to introduce new graphical capabilities to the engine. }
    \cvitem{hlslDecompiler}{Decompiler for translation of the DirectX shader bytecode to hlsl (Work in progress). }
    \section{Open Source Contributions}
    \cvitem{}{
         Contributor in the following projects: Ureq, roctogen, patch-rs, Wine-Mono, Wine-Tkg, Wine-Staging and Wrye-Bash 
    }
    
    \section{Languages}
    \cvitem{Italian}{Mother tongue.}
    \cvitem{English}{Self-assessment (Common European Framework of Reference for Languages, CEFR).}
    \cvitem{}{\begin{tabular}{l@{\hspace{.5cm}}l}
        Reading: & C1 (Proficient user)\\
        Listening: & B2 (Indipendent user)\\
        Writing: & C1 (Proficient user)\\
        Speaking: & B1 (Indipendent user)
    \end{tabular}}

    \section{Spare time activities}
    \cvitem{Hobbies}{
        Videogames: mainly strategic and RPG videogames. \newline 
        Games: Chess, Reversi, Card games   \newline
        Music: Symphonic Metal and Power Metal listener. \newline
        Open air activities: Trekking, Swimming. \newline
        Sports: Basketball, Tennis Table 
    }

    \cvitem{Interests}{Programming, Modding, History, Science, general culture.}

\end{document}